---
title: Supplementary material for `Quantifying replicability and consistency in systematic reviews`
output: 
  pdf_document: 
    latex_engine: xelatex
---

The package `metarep` is an extension to the package `meta`, which allows incorporating replicability-analysis tools to quantify consistency and replicability of treatment effect estimates in a meta-analysis. The tool was proposed by Jaljuli et. al. (submitted) for the fixed-effect and for the random-effects meta-analyses, whith or without the common-effect assumption.  

# Packages Instalation: 
Currently,  `metarep` can be downloaded from GitHub since is being processed by `CRAN`, therefore make sure that the package `devtools` is installed. `metarep` also requires the latest version of `meta` ( >= 4.11-0, available on `guithub` )

Run the following commands in $console$ to install the packages: 
```{r instalation, eval=F}
devtools::install_github( "guido-s/meta"    , force=T )
devtools::install_github( "IJaljuli/metarep", force=T )
```

# Examples: 
Here we demonstrate the approach implemented with `metrep` on several examples from the Systematic Review Cochrane Library. These examples are detailed in the paper as well, along with a demonstration of a way to incorporate our suggestions in standard meta-analysis reporting system.
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = " "
)
```

We begin with an example based on fixed-effects meta-analysis from review number CD002943: the effect of mammogram invitation on attendance during the following 12 months.

## $1^{st}$ Example: Review CD002943

```{r example_CD002943}
library(metarep)
data(CD002943_CMP001)

m2943 <- meta::metabin( event.e = N_EVENTS1, n.e = N_TOTAL1, 
                     event.c = N_EVENTS2, n.c = N_TOTAL2,
                     studlab = STUDY, comb.fixed = T , comb.random = F,
                     method = 'Peto', sm = CD002943_CMP001$SM[1],
                     data = CD002943_CMP001)

m2943

summary(m2943)
```
The replicability-analysis results follow.
```{r RA Zaykin_and_bounds22}
m2943.ra <- metarep(x = m2943 , u = 2 , common.effect = F ,t = 0.05 ,report.u.max = T)
m2943.ra
```

`metarep` allows adding replicability results to the conventional forest plots by `meta`. This can be done by simply applying `meta::forest()` on a `metarep` object. 

```{r forest, fig.width=8.5, fig.height=3}
metarep::forest(m2943.ra, layout='revman5',digits.pval = 2 , test.overall = T )
```

## $2^{nd}$ Example: Review CD007077 

The second example is based on a fixed-effects meta analysis in review CD007077. The main objective of this review is to determine whether PBI/APBI is equivalent to or better than conventional or hypo-fractionated whole breast radiotherapy (WBRT) after breast-conservation therapy for early-stage breast cancer. The primary outcome was Cosmesis. 

```{r example007077}
data(CD007077_CMP001)

m7077 <- meta::metabin( event.e = N_EVENTS1, n.e = N_TOTAL1, 
                     event.c = N_EVENTS2, n.c = N_TOTAL2,
                     studlab = STUDY, comb.fixed = T , comb.random = F,
                     method = 'MH', sm = CD007077_CMP001$SM[1],
                     data = CD007077_CMP001)

summary(m7077)
```

With the replicability analysis:

```{r forest_CD007077, fig.width=9, fig.height=3}
m7077.ra <- metarep(x = m7077 , u = 2, t = 0.05 , report.u.max = T )

metarep::forest(m7077.ra, layout='revman5',digits.pval = 2 , test.overall = T )
```


## $3^{rd}$ Example: 
Based on a random-effects meta-analysis in review CD006823, where the meta-analysis finding was statistically significant. The authors examine the effects of wound drainage after axillary dissection for breast carcinoma on the incidence of post-operative Seroma formation. 
```{r example6823}
data(CD006823_CMP001)

m6823 <- meta::metabin( event.e = N_EVENTS1, n.e = N_TOTAL1, 
                     event.c = N_EVENTS2, n.c = N_TOTAL2,
                     studlab = STUDY, comb.fixed = F , comb.random = T,
                     method = 'MH', sm = CD006823_CMP001$SM[1],
                     data = CD006823_CMP001)

m6823
```

With replicability-analysis:

```{r forest_CD6823, fig.width=10, fig.height=3}
m6823.ra <- metarep(x = m6823 , u = 2, t = 0.05, report.u.max = T )

metarep::forest(m6823.ra, layout='revman5',digits.pval = 2 , test.overall = T )
```

## $4^{th}$ Example: Review CD003366

Based on a random-effects meta-analysis in review CD003366. The authors compare chemotherapy regimens on overall effect in Leukopaenia. Pooling 28 studies, the random-effects meta-analysis fails to declare any significant difference between regimens, due to the highly-significant yet contradicting results. 

```{r example3366}
data(CD003366_CMP005)

m3366 <- meta::metabin( event.e = N_EVENTS1, n.e = N_TOTAL1, 
                     event.c = N_EVENTS2, n.c = N_TOTAL2,
                     studlab = STUDY, comb.fixed = F , comb.random = T,
                     method = 'MH', sm = CD003366_CMP005$SM[1],
                     data = CD003366_CMP005)

m3366
```

with replicability-analysis:

```{r forest_CD3366, fig.width=10, fig.height=8}
m3366.ra <- metarep(x = m3366 , u = 2 , t = 0.05, report.u.max = T )

metarep::forest(m3366.ra, layout='revman5',digits.pval = 2 , test.overall = T )
```
